Should geophysicists use the gravity disturbance or the anomaly?

### 2018-05-24 manuscript/letter.tex
Inclui os valores na conclusao sobre a modelagem da esfera

\begin{keywords}
 potential fields -- gravity disturbance -- gravity anomaly -- gravity modelling.
\end{keywords}

@@

We know empirically that $N$ is $\approx \pm 1$ m on the oceans
and reaches a maximum absolute value of $\approx 120$ m
\citep[e.g.,][]{torge2012, sanso_sideris2013}.
Fig. \ref{fig:difference} shows the absolute difference between the
gravity disturbance and the free-anomaly globally calculated
using eq. \ref{eq:difference-disturbance-free-air} and the spherical harmonic
model EIGEN-6c4 \citep{forste2014}.
In Brazil, for example, the geoidal height
varies between $\approx \pm 30$ m \citep{ibge_mapgeo2015}.
Consequently,
the maximum absolute difference between the gravity disturbance and
the free-air anomaly in Brazil,
according to eq. \ref{eq:difference-disturbance-free-air},
is $\approx 9.258$ mGal.

@@

More often than not, gravity modelling is done by computing the
vertical component of the gravitational acceleration exerted by the sources.
We have shown that, in doing so, one is actually computing the gravity
disturbance while attempting to fit a gravity anomaly.
This is a clear inconsistency.
Doing so may even result in wrong interpretations of a quantitative nature.
In Brazil, for example, the maximum difference
between the gravity disturbance and the free-air anomaly reaches 9 mGal.
Such difference at the Earth's surface may lead to
an error of XXX m in the depth-to-center estimate of a sphere with
true depth-to-center at xxx m, radius xxxx m, and density
contrast of xxx $kg.m^{-3}$.

>>>>

\begin{keywords}
 Geopotential theory -- Gravity anomalies and Earth structure -- Reference systems -- Numerical modelling.
\end{keywords}

@@

We know empirically that $N$ is $\approx \pm 1$ m on the oceans
and reaches a maximum absolute value of $\approx 120$ m
\citep[e.g.,][]{torge2012, sanso_sideris2013}.
Fig. \ref{fig:difference} shows the absolute difference between the
gravity disturbance and the free-anomaly globally calculated
using eq. \ref{eq:difference-disturbance-free-air} and the spherical harmonic
model EIGEN-6c4 \citep{forste2014}.
In Brazil, for example, the geoidal height
varies between $\approx \pm 30$ m \citep{ibge_mapgeo2015}.
Consequently,
the maximum absolute difference between the gravity disturbance and
the free-air anomaly in Brazil,
according to eq. \ref{eq:difference-disturbance-free-air},
is $\approx 9.3$ mGal.

@@

More often than not, gravity modelling is done by computing the
vertical component of the gravitational acceleration exerted by the sources.
We have shown that, in doing so, one is actually computing the gravity
disturbance while attempting to fit a gravity anomaly.
This is a clear inconsistency.
Doing so may even result in wrong interpretations of a quantitative nature.
In Brazil, for example, the maximum difference
between the gravity disturbance and the free-air anomaly reaches $\approx 9.3$ mGal.
Such difference at the Earth's surface may lead to
an error of $850$ m in the depth-to-center estimate of a sphere with true depth-to-center at $700$ m, radius $699$ m, and density contrast of $600 kg.m^{-3}$.
